Fixing Vulnerabilities Hinders Maintainability

### 2019-02-03 paper/ICPC19/icpc19.tex
toggle comments
fixing consume

\newcommand{\Sof}[1]{\textbf{[Sofia:[}{\color{red} #1}\textbf{]]}}
\newcommand{\Luis}[1]{\textbf{[Luis:[}{\color{green} #1}\textbf{]]}}
\newcommand{\Rui}[1]{\textbf{[Rui:[}{\color{blue} #1}\textbf{]]}}

@@

In the example (Listing~\ref{lst:vuln}), all functions receive as input the \textbf{handshake} represented by \texttt{s}. Every SSL/TLS connection begins with a handshake which is reponsible by the negotiation between two parties. The handshake determines what cryptographic algorithms will be used to encrypt communications, verify the server and establish a secure connection before beginning data transfer. In the \texttt{dtls1\_reassemble\_fragment} function the value of
\texttt{msg\_hdr-$>$frag\_off+frag\_len} is checked against the maximum
handshake message size, but \texttt{msg\_len} is allocated to the fragment
buffer in line $37$. Thus, if the fragment was within the allowed size, the
pending handshake message could could use up to $18MB$ ($16MB$+$2MB$). According to the
message commit, $10$ handshake messages are allowed, so the attacker could
consume until $180MB$ per DTLS connection.

@@

\noindent
We thank to the Software Improvement Group (SIG) team for all the support and
help in validating the methodology.

>>>>

%
% Add comments in the text
%
\newboolean{showcomments}
\setboolean{showcomments}{true}
%\setboolean{showcomments}{false}

\ifthenelse{\boolean{showcomments}}
  {\newcommand{\nb}[3]{
  {\color{#2}\small\fbox{\bfseries\sffamily\scriptsize#1}}
  {\color{#2}\sffamily\small$\triangleright~$\textit{\small #3}$~\triangleleft$}
  }
  }
  {\newcommand{\nb}[3]{}
  }

\newcommand\Sof[1]{\nb{Sofia}{red}{#1}}
\newcommand\Luis[1]{\nb{Luis}{green}{#1}}
\newcommand\Rui[1]{\nb{Rui}{blue}{#1}}

@@

In the example (Listing~\ref{lst:vuln}), all functions receive as input the
\textbf{handshake} represented by \texttt{s}. Every SSL/TLS connection begins
with a handshake which is reponsible by the negotiation between two parties. The
handshake determines what cryptographic algorithms will be used to encrypt
communications, verify the server and establish a secure connection before
beginning data transfer. In the \texttt{dtls1\_reassemble\_fragment} function
the value of \texttt{msg\_hdr-$>$frag\_off+frag\_len} is checked against the
maximum handshake message size, but \texttt{msg\_len} is allocated to the
fragment buffer in line $37$. Thus, if the fragment was within the allowed size,
the pending handshake message could use up to $18$MB ($16$MB+$2$MB).
According to the message commit, $10$ handshake messages are allowed. Hence,
the attacker could potentially use $180$MB per DTLS connection.

@@

\noindent
We thank the Software Improvement Group (SIG) team for all the support and
help in validating the methodology.
